---
title: "Fleet Science Center - Best Correlations"
author: "Diego Enriquez"
date: "29/9/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, warning=FALSE}
suppressMessages(library(data.table))
suppressMessages(library(lubridate))
suppressMessages(library(ggplot2))
suppressMessages(library(grid))

# Functions ==================================================================================================================================
source("fleet_func.R")
```


```{r echo=FALSE, warning=FALSE}
fleet_visitors <- readVisitorData()
```

```{r echo=FALSE, warning=FALSE}
ga_allws_nochn_all <- readQueryExplorerData("data/ga/fleet_allws_nochn_all.tsv", c("Date"))
ga_allws_nochn_os <- readQueryExplorerData("data/ga/fleet_allws_nochn_os.tsv", c("Date"))
ga_allws_nochn_us <- readQueryExplorerData("data/ga/fleet_allws_nochn_us.tsv", c("Date"))
ga_allws_nochn_do <- readQueryExplorerData("data/ga/fleet_allws_nochn_do.tsv", c("Date"))
ga_allws_nochn_lo <- readQueryExplorerData("data/ga/fleet_allws_nochn_lo.tsv", c("Date"))

ga_allws_chn_all <- readQueryExplorerData("data/ga/fleet_allws_chn_all.tsv", c("Date", "Channel"))
ga_allws_chn_os <- readQueryExplorerData("data/ga/fleet_allws_chn_os.tsv", c("Date", "Channel"))
ga_allws_chn_us <- readQueryExplorerData("data/ga/fleet_allws_chn_us.tsv", c("Date", "Channel"))
ga_allws_chn_do <- readQueryExplorerData("data/ga/fleet_allws_chn_do.tsv", c("Date", "Channel"))
ga_allws_chn_lo <- readQueryExplorerData("data/ga/fleet_allws_chn_lo.tsv", c("Date", "Channel"))

ga_admin_nochn_all <- readQueryExplorerData("data/ga/fleet_admin_nochn_all.tsv", c("Date"))
ga_admin_nochn_os <- readQueryExplorerData("data/ga/fleet_admin_nochn_os.tsv", c("Date"))
ga_admin_nochn_us <- readQueryExplorerData("data/ga/fleet_admin_nochn_us.tsv", c("Date"))
ga_admin_nochn_do <- readQueryExplorerData("data/ga/fleet_admin_nochn_do.tsv", c("Date"))
ga_admin_nochn_lo <- readQueryExplorerData("data/ga/fleet_admin_nochn_lo.tsv", c("Date"))

ga_admin_chn_all <- readQueryExplorerData("data/ga/fleet_admin_chn_all.tsv", c("Date", "Channel"))
ga_admin_chn_os <- readQueryExplorerData("data/ga/fleet_admin_chn_os.tsv", c("Date", "Channel"))
ga_admin_chn_us <- readQueryExplorerData("data/ga/fleet_admin_chn_us.tsv", c("Date", "Channel"))
ga_admin_chn_do <- readQueryExplorerData("data/ga/fleet_admin_chn_do.tsv", c("Date", "Channel"))
ga_admin_chn_lo <- readQueryExplorerData("data/ga/fleet_admin_chn_lo.tsv", c("Date", "Channel"))

ga_shows_nochn_all <- readQueryExplorerData("data/ga/fleet_shows_nochn_all.tsv", c("Date"))
ga_shows_nochn_os <- readQueryExplorerData("data/ga/fleet_shows_nochn_os.tsv", c("Date"))
ga_shows_nochn_us <- readQueryExplorerData("data/ga/fleet_shows_nochn_us.tsv", c("Date"))
ga_shows_nochn_do <- readQueryExplorerData("data/ga/fleet_shows_nochn_do.tsv", c("Date"))
ga_shows_nochn_lo <- readQueryExplorerData("data/ga/fleet_shows_nochn_lo.tsv", c("Date"))

ga_shows_chn_all <- readQueryExplorerData("data/ga/fleet_shows_chn_all.tsv", c("Date", "Channel"))
ga_shows_chn_os <- readQueryExplorerData("data/ga/fleet_shows_chn_os.tsv", c("Date", "Channel"))
ga_shows_chn_us <- readQueryExplorerData("data/ga/fleet_shows_chn_us.tsv", c("Date", "Channel"))
ga_shows_chn_do <- readQueryExplorerData("data/ga/fleet_shows_chn_do.tsv", c("Date", "Channel"))
ga_shows_chn_lo <- readQueryExplorerData("data/ga/fleet_shows_chn_lo.tsv", c("Date", "Channel"))

ga_exhib_nochn_all <- readQueryExplorerData("data/ga/fleet_exhib_nochn_all.tsv", c("Date"))
ga_exhib_nochn_os <- readQueryExplorerData("data/ga/fleet_exhib_nochn_os.tsv", c("Date"))
ga_exhib_nochn_us <- readQueryExplorerData("data/ga/fleet_exhib_nochn_us.tsv", c("Date"))
ga_exhib_nochn_do <- readQueryExplorerData("data/ga/fleet_exhib_nochn_do.tsv", c("Date"))
ga_exhib_nochn_lo <- readQueryExplorerData("data/ga/fleet_exhib_nochn_lo.tsv", c("Date"))

ga_exhib_chn_all <- readQueryExplorerData("data/ga/fleet_exhib_chn_all.tsv", c("Date", "Channel"))
ga_exhib_chn_os <- readQueryExplorerData("data/ga/fleet_exhib_chn_os.tsv", c("Date", "Channel"))
ga_exhib_chn_us <- readQueryExplorerData("data/ga/fleet_exhib_chn_us.tsv", c("Date", "Channel"))
ga_exhib_chn_do <- readQueryExplorerData("data/ga/fleet_exhib_chn_do.tsv", c("Date", "Channel"))
ga_exhib_chn_lo <- readQueryExplorerData("data/ga/fleet_exhib_chn_lo.tsv", c("Date", "Channel"))

ga_exhib2_nochn_all <- readQueryExplorerData("data/ga/fleet_exhib2_nochn_all.tsv", c("Date"))
ga_exhib2_nochn_os <- readQueryExplorerData("data/ga/fleet_exhib2_nochn_os.tsv", c("Date"))
ga_exhib2_nochn_us <- readQueryExplorerData("data/ga/fleet_exhib2_nochn_us.tsv", c("Date"))
ga_exhib2_nochn_do <- readQueryExplorerData("data/ga/fleet_exhib2_nochn_do.tsv", c("Date"))
ga_exhib2_nochn_lo <- readQueryExplorerData("data/ga/fleet_exhib2_nochn_lo.tsv", c("Date"))

ga_exhib2_chn_all <- readQueryExplorerData("data/ga/fleet_exhib2_chn_all.tsv", c("Date", "Channel"))
ga_exhib2_chn_os <- readQueryExplorerData("data/ga/fleet_exhib2_chn_os.tsv", c("Date", "Channel"))
ga_exhib2_chn_us <- readQueryExplorerData("data/ga/fleet_exhib2_chn_us.tsv", c("Date", "Channel"))
ga_exhib2_chn_do <- readQueryExplorerData("data/ga/fleet_exhib2_chn_do.tsv", c("Date", "Channel"))
ga_exhib2_chn_lo <- readQueryExplorerData("data/ga/fleet_exhib2_chn_lo.tsv", c("Date", "Channel"))

daysinfo <- data.table(Date = seq(as.Date("2017-07-01"), as.Date("2018-07-12"), by = "day"))
daysinfo$weekNum <- wday(daysinfo$Date, week_start = 1)
daysinfo$isFirstSunday <- wday(daysinfo$Date, week_start = 1) == 7 & day(daysinfo$Date) <= 7

teststart <- "2017-07-01"  # Values for Full Data
testend <- "2018-07-12" 
maxlag <- 31
visitordata <- fleet_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
```

## Admissions

#### All locations, all channels, SessionsNew, corr: 0.932

```{r echo=FALSE, fig.width=10, warning=FALSE}
plotLagComparison(movingAverage(ga_admin_nochn_all[Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "SessionsNew",
                    dlag = 0)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(movingAverage(ga_admin_nochn_all[Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "SessionsNew",
                    dlag = 0)
```

#### Exhibitions shows a high correlation too, but with UsersOld
All locations, all channels, UsersOld, corr: 0.896

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
plotLagComparisonSameScale(movingAverage(ga_exhib2_nochn_all[Date >= teststart & Date <= testend]),
                    movingAverage(visitordata),
                    metric = "UsersOld",
                    dlag = 0)
```


```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
teststart <- "2017-07-01"  # Values for Full Data
testend <- "2018-06-11" 
maxlag <- 31
visitordata <- fleet_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_admin_nochn_all[Date >= teststart & Date <= testend]),
                                      visitors = movingAverage(visitordata)),
                 select = "SessionsNew",
                 plottitle = "")
```


#### Without moving average

```{r echo=FALSE, fig.width=10, warning=FALSE}
teststart <- "2017-07-01"  # Values for Full Data
testend <- "2018-07-12" 
maxlag <- 31
visitordata <- fleet_visitors[Date >= teststart & Date <= as.Date(testend) + maxlag]
plotLagComparison(ga_admin_nochn_all[Date >= teststart & Date <= testend],
                    visitordata,
                    metric = "SessionsNew",
                    dlag = 0)
```

#### All locations, Organic Search, UniquePageviews, corr: 0.830

```{r echo=FALSE, fig.width=10, warning=FALSE}
# plotLagComparison(movingAverage(ga_allws_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "UniquePageviews",
#                     dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotLagComparisonSameSacle(movingAverage(ga_allws_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "UniquePageviews",
#                     dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_allws_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                                       visitors = movingAverage(visitordata)),
#                  select = "UniquePageviews",
#                  plottitle = "")
```

#### Domestics, Organic Search, UniquePageviews, corr: 0.819

```{r echo=FALSE, fig.width=10, warning=FALSE}
# plotLagComparison(movingAverage(ga_allws_chn_do[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "UniquePageviews",
#                     dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotLagComparisonSameSacle(movingAverage(ga_allws_chn_do[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "UniquePageviews",
#                     dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_allws_chn_do[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                                       visitors = movingAverage(visitordata)),
#                  select = "UniquePageviews",
#                  plottitle = "")
```


## Plan your visit

#### All locations, Organic Search, Users, corr: 0.792

```{r echo=FALSE, fig.width=10, warning=FALSE}
# plotLagComparison(movingAverage(ga_plan_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "Users",
#                     dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotLagComparisonSameSacle(movingAverage(ga_plan_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "Users",
#                     dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_plan_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                                       visitors = movingAverage(visitordata)),
#                  select = "Users",
#                  plottitle = "")
```

#### United States, Organic Search, UniquePageviews, corr: 0.792

```{r echo=FALSE, fig.width=10, warning=FALSE}
# plotLagComparison(movingAverage(ga_plan_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "UniquePageviews",
#                     dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotLagComparisonSameSacle(movingAverage(ga_plan_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "UniquePageviews",
#                     dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_plan_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                                       visitors = movingAverage(visitordata)),
#                  select = "UniquePageviews",
#                  plottitle = "")
```

#### Domestics, Organic Search, Users, corr: 0.779

```{r echo=FALSE, fig.width=10, warning=FALSE}
# plotLagComparison(movingAverage(ga_plan_chn_do[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "Users",
#                     dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotLagComparisonSameSacle(movingAverage(ga_plan_chn_do[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "Users",
#                     dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_plan_chn_do[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                                       visitors = movingAverage(visitordata)),
#                  select = "Users",
#                  plottitle = "")
```


## Tickets

#### United States, Organic Search, Users, corr: 0.822

```{r echo=FALSE, fig.width=10, warning=FALSE}
# plotLagComparison(movingAverage(ga_tickets_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "Users",
#                     dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotLagComparisonSameSacle(movingAverage(ga_tickets_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "Users",
#                     dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_tickets_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                                       visitors = movingAverage(visitordata)),
#                  select = "Users",
#                  plottitle = "")
```

#### United States, All channels, UsersOld, corr: 0.819

```{r echo=FALSE, fig.width=10, warning=FALSE}
# plotLagComparison(movingAverage(ga_tickets_nochn_us[Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "UsersOld",
#                     dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotLagComparisonSameSacle(movingAverage(ga_tickets_nochn_us[Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "UsersOld",
#                     dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_tickets_nochn_us[Date >= teststart & Date <= testend]),
#                                       visitors = movingAverage(visitordata)),
#                  select = "UsersOld",
#                  plottitle = "")
```

#### All locations, Organic Search, Users, corr: 0.819

```{r echo=FALSE, fig.width=10, warning=FALSE}
# plotLagComparison(movingAverage(ga_tickets_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "Users",
#                     dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotLagComparisonSameSacle(movingAverage(ga_tickets_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "Users",
#                     dlag = 1)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_tickets_chn_all[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                                       visitors = movingAverage(visitordata)),
#                  select = "Users",
#                  plottitle = "")
```


## Visit

#### United States, All channels, Sessions, corr: 0.789

```{r echo=FALSE, fig.width=10, warning=FALSE}
# plotLagComparison(movingAverage(ga_visit_nochn_us[Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "Sessions",
#                     dlag = 2)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotLagComparisonSameSacle(movingAverage(ga_visit_nochn_us[Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "Sessions",
#                     dlag = 2)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_visit_nochn_us[Date >= teststart & Date <= testend]),
#                                       visitors = movingAverage(visitordata)),
#                  select = "Sessions",
#                  plottitle = "")
```

#### United States, Organic Search, Sessions, corr: 0.788

```{r echo=FALSE, fig.width=10, warning=FALSE}
# plotLagComparison(movingAverage(ga_visit_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "Sessions",
#                     dlag = 2)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotLagComparisonSameSacle(movingAverage(ga_visit_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "Sessions",
#                     dlag = 2)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_visit_chn_us[Channel == "Organic Search" & Date >= teststart & Date <= testend]),
#                                       visitors = movingAverage(visitordata)),
#                  select = "Sessions",
#                  plottitle = "")
```

#### All locations, All channels, Sessions, corr: 0.779

```{r echo=FALSE, fig.width=10, warning=FALSE}
# plotLagComparison(movingAverage(ga_visit_nochn_all[Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "Sessions",
#                     dlag = 2)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotLagComparisonSameSacle(movingAverage(ga_visit_nochn_all[Date >= teststart & Date <= testend]),
#                     movingAverage(visitordata),
#                     metric = "Sessions",
#                     dlag = 2)
```

```{r echo=FALSE, fig.width=10, fig.height=2.5, warning=FALSE}
# plotCorrelations(getCorrelationMatrix(gametrics = movingAverage(ga_visit_nochn_all[Date >= teststart & Date <= testend]),
#                                       visitors = movingAverage(visitordata)),
#                  select = "Sessions",
#                  plottitle = "")
```